### 2017-06-18 src/algorithm.tex
alg

In this section we present an FPTAS algorithm to the \VPN problem.
We are given an instance of the \VPN problem 
\begin{align*}
D_v = (V_v, A_v)		\\
D_p = (V_p, A_p)		\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c, c)
\end{align*}
For now assume all values are integral and polynomial bounded in the size of the input.

Let $T_{v_p}(u_v, w_v, C)$ denote the minimum processing required to embed
all the virtual vertices, excluding $u_v$, on a $u_vw_v$-path into the physical
vertex $v_p$ with cost constraint $C$.
$T$ can be computed recursively as follow:
\begin{align*}
&T_{v_p}(u_v, w_v, C) = 
\min_{v_vv_v \in A_v} T_{v_p}(u_v, v_v, C - c(w_v, v_p))
\\
&T(u_v, u_v, C) = 0
\\
&T(-, -, 0) = \infty
\end{align*}

Let $O(v_v, v_p)$ denote the optimal embedding of a $s_vv_v$-path into a
$s_pv_p$-path.
Let $pi:V_v \to \N$ be any typological ordering of $V_v$. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&O(v_v, v_p) = 
\min_{\substack{
u_v : pi(u_v) < pi(v_v), 
\\
u_pv_p \in A_p
}}
O(u_v, u_p)
+
\argmin_{C : T_{v_p}(u_v, v_v, C) \leq p_c(v_p)}
\\
&O(s_v, v_p) = c(s_v, v_p)
\end{align*}

% For a physical vertex $v_p$ we define 
% $c_{v_p}(u_v, v_v):A_v \to \R = c(v_v, v_p)$.
% Given two virtual vertices $s'_v, t'_v$ and a physical vertex $v_p$, 
% one can verify that the minimum cost of embedding any 
% 
% 
% we would like to find an optimal embedding of an $s'_vt'_v$-path into
% $v_p$.
% A solution to this sub-problem can be found as follow:
% First we build the \emph{cost graph} correspond to $s'_v, t'_v$ and $v_p$, 
% the cost graph is a graph that lets us (efficiently) compute the cost of em  
% 
% For a vertex $v$ let $C(v)$ be the set of its children.
% Let $O'(s'_v, t'_v, s'_p, t'_p)$ be the optimal embedding of some virtual
% $C(s'v)t'_v$-path into the physical vertex $t'_p$ such that the bottleneck
% between $s'_p$ and $t'_p$ is at least $b_d(s'_v, t'_v)$.
% Let $c_v \in C(s'_v)$ and observe that once $c_v$ is chosen the arc 
% $(s'_v, c_v)$ determines completely whether a physical path with a feasible
% bottleneck exists, namely, 
% a physical path exists if and only if there is a physical $s'_vt'_v$-path containing only
% arcs with bandwidth at least $b_d(s'_v, c_v)$.
% On the other hand, the set of $c_vt'_v$-paths
% determine completely the cost (and processing-wise feasibility) of the embedding.
% Figure depicts the above observations.
% 
% \begin{figure}[ht]
% \centering
% \input{fig-dp}
% \caption[]{
% \begin{enumerate*}
% \item Computing $O'(s'_v, t'_v, s'_p, t'_p)$.
% \item The set of $c_dt'_v$-paths determines completely the cost of the embedding
% \item 
% The arc $(s'_v, c_d)$ determines completely the connectivity of $s'_p$ and
% $t'_p$, i.e. physical arcs with bandwidth less than $b_d(s'_v, c_d)$ can not be
% used.
% \end{enumerate*}
% }
% \end{figure}
% 
% Among all the $c_vt'_v$-paths we want to select the one that minimize the
% embedding cost under the processing capacity constraints.
% This can be done... 
% Calculating $O'(s'_v, t'_v, s'_p, t'_p)$ can be done simply by finding the
% optimal path among all children of $s'_v$.
% 
% Let $O(t'_v, t'_p)$ be the optimal embedding of some virtual $s_vt'_v$-path
% into some physical $s_pt'_p$-path then $O(t_v, t_p)$ is the global optimal
% embedding.
% Also $O(t'_v, s_p)$ can be computed efficiently for every $t'_v$ as described
% above, and $O(s_v, t'_v)$ is simply the minimum cost of embedding $s_v$ in any
% physical vertex $s'_p$ such that a physical $s'_pt'_v$-path exists.
% For an arbitrary vertices $t'_v$, and $t'_p$, $O(t'_v, t'_p)$ can be computed
% efficiently using dynamic programming with the following recursion formula:
% $$
% O(t'_v, t'_p) = 
% \min_{\substack{
% s'_v \in P(t'_v)
% \\
% s'_p \in P(t'_p)
% }}
% O(s'_v, s'_p) + O'(s'_v, t'_v, s'_p, t'_p)
% $$ 
% 
%

>>>>

In this section we present an FPTAS algorithm to the \VPN{} problem.
We are given an instance of the \VPN{} problem 
\begin{align*}
D_v = (V_v, A_v)		\\
D_p = (V_p, A_p)		\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c, c)
\end{align*}
For now, assume all values are integral and polynomial bounded in the size of
the input.
Under this assumption we show that an optimal embedding can be computed
efficiently.
We then argue that, using a standard scaling and rounding technique, we can use
the same computation to achieve a solution with a cost only
$1 + \varepsilon$ times greater that of the optimal solution, for any
$\varepsilon > 0$.
Also, for convenient and w.l.o.g, assume that $s_v, t_v$ are dummy vertices, 
i.e. $c(s_v, v_p) = c(t_v, v_p) = 0$ for every $v_p \in V_p$.

We start by arguing that the minimum processing time required to embed some
$u_vw_v$-path into a vertex $v_p$ can be computed efficiently.
Let $P_{v_p}(u_v, w_v, C)$ denote the minimum processing required to embed
all the virtual vertices, excluding $u_v$, on a $u_vw_v$-path into the physical
vertex $v_p$ with cost constraint $C$.
$P$ can be computed recursively as follow:
\begin{align*}
&P_{v_p}(u_v, w_v, C) = 
\min_{v_vv_v \in A_v} P_{v_p}(u_v, v_v, C - c(w_v, v_p))
\\
&P(u_v, u_v, C) = 0
\\
&P(-, -, <0) = \infty
\end{align*}

We now show how to compute the optimal embedding.
Let $C(w_v, w_p)$ denote the
optimal embedding of a $s_vw_v$-path into a $s_pw_p$-path.
Let $\pi:V_v \to \N$ be any typological ordering of $V_v$. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&C(w_v, w_p) = 
\min_{\substack{
u_v : pi(u_v) \leq pi(v_v), 
\\
v_pw_p \in A_p
}}
C(u_v, u_p)
+
\argmin_{C : P_{w_p}(v_v, w_v, C) \leq p_c(w_p)}
\\
&C(s_v, w_p) = c(s_v, w_p)
\end{align*}
We note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $u_vv_v$ with bandwidth greater than
$b_c(v_p, w_p)$ from the virtual graph and only then compute $P_{w_p}(v_v, w_v,
C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.

\begin{figure}[ht]
\centering
\input{fig-dp1}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $s_vw_v$-path into a $s_pw_p$ path can be efficiently 
computed by breaking the problem into the problem of embedding a $s_vu_v$-path
into a $s_pv_p$-path (blue, dashed rectangles) 
and the problem of embedding a $u_vw_v$-path into $w_p$ (red, dotted
rectangles) where $b_d(u_v, v_v) \leq b_c(v_p, w_p)$.
}
\end{figure}

### 2017-06-18 src/latency.tex
fix errors
alg

\todo{Are we going to talk about the problem also with latency constraint ?}
We now extend the problem by adding a global latency constraint.
Formally, we are given a latency function $l : A_v \times A_p \to \R$,
and a latency constraint $L$.
The goal is to find a min-cost embedding that also respect the latency
constraint.
Observe that given two physical vertices $s_p$, $t_p$ and a virtual edge $e_v$
a $s_pt_p$-path that minimize the latency can be efficiently found by using any
standard shortest path algorithm where the "distance" function is replaced by
the appropriate latency.
Observe that this can also be done if we restrict ourselves to use only physical
edges with a lower bound on their bandwidth.
We now show that if all values are integral and polynomial bounded, we can
efficiently find a feasible embedding with a cost bounded by $C$ that minimize
the latency.

Let $O(t'_v, t'_p, C)$ be an embedding of some virtual $s_vt'_v$-path 
into a physical $s_pt'_p$-path that has cost not more than $C$ and that
minimizes the latency.

>>>>

We now extend the problem by adding a global latency constraint.
Formally, we are given a latency function $l : A_v \times A_p \to \R$,
and a latency constraint $L$.
The goal is to find a min-cost embedding that also respect the latency
constraint.
Observe that given two physical vertices $s_p$, $t_p$ and a virtual edge $e_v$
a $s_pt_p$-path that minimize the latency can be efficiently found by using any
standard shortest path algorithm where the "distance" function is replaced by
the appropriate latency.
Observe that this can also be done if we restrict ourselves to use only physical
edges with a lower bound on their bandwidth.
We now show that if all values are integral and polynomial bounded, we can
efficiently find a feasible embedding with a cost bounded by $C$ that minimize
the latency.

Let $L(w_v, w_p, C)$ denote the minimum possible latency result from an
embedding of some virtual $s_vw_v$-path into a physical $s_pw_p$-path 
that has cost not more than $C$.

We claim that $L(w_v, w_p, C)$ can be computed efficiently as follow:
\begin{align*}
&L(w_v, w_p, C) = \min_{\substack{
u_v : pi(u_v) \leq pi(v_v), 
\\
v_pw_p \in A_p
\\
\delta : P(u_v, w_v, \delta) \leq p_c(w_p)
}}
l(v_p, w_p) + L(u_v, v_p, C - \delta)
\\
&L(s_v, w_p, >=0) = 0
\\
&L(-, -, <0) = \infty
\end{align*}

Now, to compute the optimal embedding with the additional latency constraint,
$L$, one can simply (binary) search for the minimum value of $C$ such that
$L(t_v, t_p, C) \leq L$.
